---
title: "PSTAT 126 - Project Step 1"
author: Orion Marini & Sara Chong
date: "2023-11-05"
output:
  pdf_document: 
    latex_engine: xelatex
  html_document:
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(modelr)
library(faraway)
library(skimr)
library(tinytex)
library(ggplot2)
options(scipen = 999)
```

## Descriptor  

The California House Pricing Dataset from Kaggle encapsulates a snapshot of houses within specific Californian blocks as recorded during the 1990 census. The dataset encompasses a range of attributes that define these housing units, and we focus on two key variables: median housing value and median income. These variables of interest offer valuable insights into the dynamics of the housing market in California. As we explore this dataset, we aim to understand the relationship between median housing value and median income, hypothesizing that these two variables are positively correlated.

```{r initilization, echo=FALSE}
complete_housing_dataset<-read_csv('C:/Users/orion/Documents/PSTAT126/housing.csv', show_col_types = FALSE)
set.seed(1)
hdr<- sample(1:nrow(complete_housing_dataset), 500, replace=FALSE)
data_sample <- complete_housing_dataset[hdr,]
```

```{r checks, echo=FALSE}
plot(data_sample$median_income, data_sample$median_house_value, 
     xlab = "Median House Income", ylab = "Median House Value", 
     main = "Scatter Plot of the Relationship Between Variables")
lin_reg_model <- lm(data_sample$median_house_value ~ data_sample$median_income, data = data_sample)
abline(lin_reg_model, col = "red")
correlation <- cor(data_sample$median_income, data_sample$median_house_value)
summary(lin_reg_model)
```

```{r assumptions, echo=FALSE}
residuals <- residuals(lin_reg_model)
plot(predict(lin_reg_model), residuals, xlab = "Prediction of Y", ylab="Residuals", main="Residuals vs Predicted Plot")
```
